DNA meth and IVF

### 2023-12-19 figs/art_example.Rmd
art example

sig <- subset(mtable,p.adjustMANOVA<0.05)
plot(mtable$s.Discovery,mtable$s.Replication,pch=19,col="gray",
  xlab="Estill 450k",ylab="Novakovic EPIC",main="pathway enrichment score")
points(sig$s.Discovery,sig$s.Replication,pch=19,col="red")
abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")

pdf("fig7b.pdf")
plot(mtable$s.Discovery,mtable$s.Replication,pch=19,col="gray",
  xlab="Estill 450k",ylab="Novakovic EPIC",main="pathway enrichment score")
points(sig$s.Discovery,sig$s.Replication,pch=19,col="red")
abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
dev.off()

@@

k <- MASS::kde2d(det[,1], det[,2])
X_AXIS = "Discovery"
Y_AXIS = "Replication"

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Creation of C4 and C2 Activators", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Creation of C4 and C2 Activators", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()

@@

mitch_report(res=mres,outfile="aging_mitchreport.html",overwrite=TRUE)
mitch_plots(res=mres,outfile="aging_mitchcharts.pdf")

@@

save.image("aging_example.Rdata")

>>>>

sig <- subset(mtable,p.adjustMANOVA<0.05)
plot(mtable$s.Estill,mtable$s.Novakovic,pch=19,col="gray",
  xlab="Estill 450k",ylab="Novakovic EPIC",main="pathway enrichment score")
points(sig$s.Estill,sig$s.Novakovic,pch=19,col="red")
abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")

pdf("fig7b.pdf")
plot(mtable$s.Estill,mtable$s.Novakovic,pch=19,col="gray",
  xlab="Estill 450k",ylab="Novakovic EPIC",main="pathway enrichment score")
points(sig$s.Estill,sig$s.Novakovic,pch=19,col="red")
abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
dev.off()

@@

k <- MASS::kde2d(det[,1], det[,2])
X_AXIS = "Estill 450k"
Y_AXIS = "Novakovic EPIC"

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()

@@

mitch_report(res=mres,outfile="art_mitchreport.html",overwrite=TRUE)
mitch_plots(res=mres,outfile="art_mitchcharts.pdf")

@@

save.image("art_example.Rdata")
